---
title: "One of Two? Visual dependency in dynamic scenes."
author: "Candan A.Ş., Aydın T., Özkan Z.G."
date: "2023-04-17"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE, message = F}
knitr::opts_chunk$set(root.dir = dirname(rstudioapi::getSourceEditorContext()$path))
library(tidyverse)
library(ggpubr)
library(ez)
library(ggplot2)
library(readxl)
library(stringr)
library(readr)
library(rstatix)
library(qqplotr)
library(DescTools)
```

## Main raw data column explanation

```{file description}
Participant:            participant number
Condition:              order type of the videos
Perspective:            perspectives
Activity:               action type made by actors in videos
Actor:                  actor group
Shot_Type:              type of shots
movie_resp.keys:        button pressed by the participants to answer video memory part
movie_resp.corr:        participants accuracy in video memory part
movie_resp.rt:          participants reaction time in video memory part
trials.thisIndex:       number of shot
corrAnsw:               correct answers in video memory part
corrAnsIM:              correct answers in image memory part
IM_key.keys:            button pressed by the participants to answer image memory part
IM_key.corr:            participants accuracy in image memory part
IM_key.rt:              participants reaction time in image memory part
```

## Variable names explanation

```{Variable names explanation}
Note: Video memory and image memory, which were decided as analysis names at the beginning of the article, were later changed to shot memory and spatial orientation memory respectively.

dprimes:               data frame for d prime scores, criterion c scores, z-scores, means, standard deviations, standart errors for video memory data
VDdprime:              2*2 mixed design analysis of variance for d prime scores
VDrt:                  2*2 mixed design analysis of variance for video memory reaction time
partialE_cond_vd_d:    partial eta square for condition variable on video memory d prime scores
partialE_Pers_vd_d:    partial eta square for perspective variable on video memory d prime scores
partialE_inter_vd_d:   partial eta square for interaction on video memory d prime scores
partialE_cond_vd_rt:   partial eta square for condition variable on video memory reaction times
partialE_Pers_vd_rt:   partial eta square for perspective variable on video memory reaction times
partialE_inter_vd_rt:  partial eta square for interaction on video memory reaction times
Image_M:               data frame for means, standard deviations, standard errors for image memory data
AccIM:                 2*2 mixed design analysis of variance for image memory accuracies
partialE_cond_acc_IM:  partial eta square for condition variable on image memory accuracies
partialE_Pers_acc_IM:  partial eta square for perseption variable on image memory accuracies
partialE_inter_acc_IM: partial eta square for interaction on image memory accuracies
IMrt:                  2*2 mixed design analysis of variance for image memory reaction times
partialE_cond_rt_IM:   partial eta square for condition variable on image memory reaction times
partialE_Pers_rt_IM:   partial eta square for perseption variable on image memory reaction times
partialE_inter_rt_IM:  partial eta square for interaction on image memory reaction times
Awareness:             data frame for awareness in post questionnaire
```

```{r load data, include=FALSE}
#Please note, Since the z-score of the 16th participant's reaction time in two perspectives was higher than 3.92, it was excluded from the data as outlier.

####    Video Memory    ####
#source("prec.R")
#raw_data = preproc(data_dir = "Results")
#save(raw_data, file= "raw_data.Rda")
#or
load("raw_data.Rda")

####    Image Memory    ####
#source("precIM.R")
#raw_dataIM = precIM(data_dir = "Results")
#save(raw_dataIM, file= "raw_dataIM.Rda")
# or
load("raw_dataIM.Rda")

####    Awareness    ####
Awareness <- read_excel("Awareness.xlsx")
```

```{r setup2, include=FALSE, cache=FALSE}
options(scipen = 1, digits = 3)
```


# 1. D prime and Accuracy Analysis

## 1.1. Data preparetion

```{r D prime and Accuracy Analysis}
# n_hit/n_miss/n_fa/n_cr & d'primes

dprimes <- raw_data %>% 
  group_by(Participant,Perspective,Condition) %>% 
  summarise(
    n_hit = sum(movie_resp.corr == 1 & Shot_Type == "test shot"),
    n_miss = sum(movie_resp.corr == 0 & Shot_Type == "test shot"),
    n_fa = sum(movie_resp.corr == 0 & Shot_Type == "distractor shot"),
    n_cr = sum(movie_resp.corr == 1 & Shot_Type == "distractor shot")) %>% 
  group_by(Participant,Perspective) %>% 
  mutate(hitrate = (n_hit+0.5)/((n_hit+0.5)+(n_miss+0.5)), farate = (n_fa+0.5)/((n_fa+0.5)+(n_cr+0.5))) %>% 
  mutate(zscoreHit = qnorm(hitrate), zscoreFA = qnorm(farate)) %>% 
  mutate(dprime = zscoreHit - zscoreFA) %>% 
  mutate(CriterionC = -0.5*(zscoreHit+zscoreFA))

dprimes1 <- raw_data %>% 
  group_by(Participant,Perspective) %>% 
  summarise(meanrt = mean(movie_resp.rt))

dprimes <- dprimes %>% 
  left_join(dprimes1,by=c("Participant","Perspective"))

Image_M <- raw_dataIM %>% 
  group_by(Participant,Perspective,Condition,Gender,Age) %>% 
  summarise(accuracy_M = mean(IM_key.corr),
            rt_M = mean(IM_key.rt),
            rt_sd = sd(IM_key.rt))

```

## 1.2. Contrasting

```{r Contrasting}
dprimes$Condition <- as.factor(dprimes$Condition)
levels(dprimes$Condition)
contrasts(dprimes$Condition)

dprimes$Perspective <- factor(dprimes$Perspective,levels= c("Single", "Shot-Reverse-Shot"))
levels(dprimes$Perspective)
contrasts(dprimes$Perspective)

Image_M$Condition <- as.factor(Image_M$Condition)
levels(Image_M$Condition)
contrasts(Image_M$Condition)

Image_M$Perspective <- factor(Image_M$Perspective, levels= c("Single", "Shot-Reverse-Shot"))
levels(Image_M$Perspective)
contrasts(Image_M$Perspective)
```

## 1.3. ANOVAs

### 1.3.1. D prime

```{r ANOVAs}
VDdprime<-ezANOVA(data = dprimes,
        dv = dprime,
        wid=Participant,
        within = Perspective,
        between = Condition,
        type = 3,
        detailed = TRUE,
        return_aov = TRUE);VDdprime
```

Partial Eta Squares

```{r effect sizes1,include=FALSE}
partialE_cond_vd_d <- VDdprime$ANOVA$SSn[2] / (VDdprime$ANOVA$SSd[2] + VDdprime$ANOVA$SSn[2])
partialE_Pers_vd_d <- VDdprime$ANOVA$SSn[3] / (VDdprime$ANOVA$SSd[3] + VDdprime$ANOVA$SSn[3])
partialE_inter_vd_d <- VDdprime$ANOVA$SSn[4] / (VDdprime$ANOVA$SSd[4] + VDdprime$ANOVA$SSn[4])
```

### 1.3.2. RT - video memory -

```{r Anovas2}
VDrt<-ezANOVA(data = dprimes,
           dv = meanrt,
           wid=Participant,
           within = Perspective,
           between = Condition,
           type = 3,
           detailed = TRUE,
           return_aov = TRUE);VDrt
```

Partial Eta Squares

```{r etas2,include=FALSE}
partialE_cond_vd_rt <- VDrt$ANOVA$SSn[2] / (VDrt$ANOVA$SSd[2] + VDrt$ANOVA$SSn[2])
partialE_Pers_vd_rt <- VDrt$ANOVA$SSn[3] / (VDrt$ANOVA$SSd[3] + VDrt$ANOVA$SSn[3])
partialE_inter_vd_rt <- VDrt$ANOVA$SSn[4] / (VDrt$ANOVA$SSd[4] + VDrt$ANOVA$SSn[4])
```

### 1.3.3. Accuracy

```{r Anovas3}
AccIM<-ezANOVA(data=Image_M,
        dv = accuracy_M,
        wid=Participant,
        within = Perspective,
        between = Condition,
        detailed = TRUE,
        return_aov = TRUE,
        type=3);AccIM
```

Partial Eta Squares

```{r etas4,include=FALSE}
partialE_cond_acc_IM <- AccIM$ANOVA$SSn[2] / (AccIM$ANOVA$SSd[2] + AccIM$ANOVA$SSn[2])
partialE_Pers_acc_IM <- AccIM$ANOVA$SSn[3] / (AccIM$ANOVA$SSd[3] + AccIM$ANOVA$SSn[3])
partialE_inter_acc_IM <- AccIM$ANOVA$SSn[4] / (AccIM$ANOVA$SSd[4] + AccIM$ANOVA$SSn[4])
```

### 1.3.4. RT - image memory -

```{r Anovas4}
IMrt<-ezANOVA(data=Image_M,
        dv = rt_M,
        wid=Participant,
        within = Perspective,
        between = Condition,
        detailed = TRUE,
        return_aov = TRUE,
        type=3);IMrt
```

Partial Eta Squares

```{r etas5,include=FALSE}
partialE_cond_rt_IM <- IMrt$ANOVA$SSn[2] / (IMrt$ANOVA$SSd[2] + IMrt$ANOVA$SSn[2])
partialE_Pers_rt_IM <- IMrt$ANOVA$SSn[3] / (IMrt$ANOVA$SSd[3] + IMrt$ANOVA$SSn[3])
partialE_inter_rt_IM <- IMrt$ANOVA$SSn[4] / (IMrt$ANOVA$SSd[4] + IMrt$ANOVA$SSn[4])
```

## 1.3.5 Partial Eta Squares

```{r etas6, include=FALSE}
# Eta Squares Table
sqr<- c(partialE_cond_vd_d,partialE_Pers_vd_d,partialE_inter_vd_d,partialE_cond_vd_rt,partialE_Pers_vd_rt,partialE_inter_vd_rt,
                partialE_cond_acc_IM,partialE_Pers_acc_IM,partialE_inter_acc_IM,partialE_cond_rt_IM,partialE_Pers_rt_IM,partialE_inter_rt_IM)
nm <- c("VideoMemory_Dprime_Order","VideoMemory_Dprime_Pers","VideoMemory_Dprime_Inter","VideoMemory_RT_Order","VideoMemory_RT_Pers","VideoMemory_RT_Inter",
                "ImageMemory_Accuracy_Order","ImageMemory_Accuracy_Pers","ImageMemory_Accuracy_Inter","ImageMemory_RT_Order","ImageMemory_RT_Pers","ImageMemory_RT_Inter")
SqrTable <- data.frame(row.names = c("name","eta_sq"))
SqrTable <- data.frame(name = nm,eta_sq = sqr)
```

```{r Eta sqr tables}
tibble(SqrTable)
```

# 2. Awareness

```{r Post-experiment Questions}
Awareness <- Awareness %>% group_by(AwarenessType,Question) %>% mutate(means = (sum(First,na.rm = TRUE)/62)*100)
```

# 3. Visualizations

## 3.1. Awareness Plot

```{r Post-experiment Questions2, echo=FALSE}
bargraph_awareness = ggplot(Awareness %>% group_by(AwarenessType,Question), aes(y=means, x=AwarenessType, fill = as.factor(Question)))+
  geom_bar(position=position_dodge(1), stat="identity",width = 0.9)+
  scale_fill_manual(name="Question", values = c("#999999", "#666666","#333333"),
                    labels = c("first", "second","third")) + 
  xlab("Awareness Type") +
  ylab("% of Participants") + 
  theme(text=element_text(size=12,
                          family="Arial"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_text(size = 10),
        panel.background = element_rect(colour = "black", size=1.3, fill=NA),
        #legend.position = c(0.8,0.8),
        legend.position = "top",
        aspect.ratio = 1) + 
  coord_cartesian(ylim = range(0:100)) +
  scale_y_continuous(expand = c(0,0.4))+
  geom_text(aes(label=round(means,2)), position=position_dodge(width=1), vjust=2,col = "white");bargraph_awareness

```

## 3.2. D'scores

```{r D scores Viz,echo=FALSE}
dprimes <- dprimes %>% group_by(Perspective,Condition) %>% mutate(meand = mean(dprime),
                                                                   sd = sd(dprime),
                                                                   n = n())
                                                                
dprimes$se = dprimes$sd/sqrt(dprimes$n)

Image_M <- Image_M %>% group_by(Perspective,Condition) %>% mutate( accuracy_M_M = mean(accuracy_M),
                                                         sdAcc = sd(accuracy_M),
                                                         n = n(),
                                                         rt_M_M = mean(rt_M),
                                                         sdRT_sd = sd(rt_M))
Image_M$se = Image_M$sdAcc/sqrt(Image_M$n)

bargraph_dprime = ggplot(dprimes %>% group_by(Perspective,Condition), aes(y=dprime, x=Perspective, fill = Condition, ymax= meand + se, ymin= meand - se))+
  stat_summary(fun.y = mean, 
               geom = "bar", 
               position=position_dodge(0.7),
               width = 0.6) + 
  geom_errorbar(position = position_dodge(0.7), 
                width = 0.2)+
  scale_fill_manual(name="Order", values = c("#666666", "#999999"),
                    labels = c("Canonical", "Scrambled")) + 
  xlab("Perspective") +
  ylab("D prime scores") + 
  theme(text=element_text(size=12,
                          family="Arial"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_text(size = 10),
        panel.background = element_rect(colour = "black", size=1.3, fill=NA),
        legend.position = "top",
        #legend.position = c(0.7,0.86),
        legend.box = "vertical",
        aspect.ratio = 1) +
  coord_cartesian(ylim = range(0:2.5)) +
  scale_y_continuous(expand = c(0,0.005))

bargraph_dprime<-bargraph_dprime +
  geom_line(data = tibble(x=c(1,2), y = c(1.75,1.75)), aes(x=x,y=y), 
           inherit.aes = F)+
  geom_text(data = tibble(x=1.5, y = 1.8), aes(x=x,y=y), 
            inherit.aes = F,label = "* * *",size = 5)+
  geom_line(data = tibble(x=c(1,1), y = c(1.75,1.65)), aes(x=x,y=y), 
            inherit.aes = F)+
  geom_line(data = tibble(x=c(2,2), y = c(1.75,1.65)), aes(x=x,y=y), 
            inherit.aes = F);bargraph_dprime
```

## 3.3. Image Memory

```{r Image M Viz, echo=FALSE}
bargraph_image_m = ggplot(Image_M %>% group_by(Perspective,Condition), aes(y=accuracy_M, x=Perspective, fill = Condition,ymax= accuracy_M_M + se, ymin= accuracy_M_M - se))+
  coord_cartesian(ylim = c(0.5,1))+
  stat_summary(fun = mean,
               geom = "bar",
               position=position_dodge(0.7),
               width = 0.6) +
  geom_errorbar(position = position_dodge(0.7),
                width = 0.2)+
  scale_fill_manual(name="Order", values = c("#666666", "#999999"),
                    labels = c("Canonical", "Scrambled")) + 
  xlab("Perspective") +
  ylab("% of Accuracy") + 
  theme(text=element_text(size=12,
                          family="Arial"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_text(size = 10),
        panel.background = element_rect(colour = "black", size=1.3, fill=NA),
        #legend.position = c(0.7,0.86),
        legend.position = "top",
        legend.box = "vertical",
        aspect.ratio = 1)+
  scale_y_continuous(expand = c(0,0.004),)

bargraph_image_m <- bargraph_image_m + 
  geom_line(data = tibble(x=c(1,2), y = c(0.97,0.97)), aes(x=x,y=y), 
            inherit.aes = F)+
  geom_text(data = tibble(x=1.5, y = 0.974), aes(x=x,y=y), 
            inherit.aes = F,label = "* * *",size = 5)+
  geom_line(data = tibble(x=c(1,1), y = c(0.97,0.955)), aes(x=x,y=y), 
            inherit.aes = F)+
  geom_line(data = tibble(x=c(2,2), y = c(0.97,0.955)), aes(x=x,y=y), 
            inherit.aes = F);bargraph_image_m
```

# 4. Gender, Age and Activity

## 4.1. Data preparetion
```{r DP for gender Age}
dprimes_gender <- raw_data %>% group_by(Participant,Gender,Age) %>% summarise(
  n_hit = sum(movie_resp.corr == 1 & Shot_Type == "test shot"),
  n_miss = sum(movie_resp.corr == 0 & Shot_Type == "test shot"),
  n_fa = sum(movie_resp.corr == 0 & Shot_Type == "distractor shot"),
  n_cr = sum(movie_resp.corr == 1 & Shot_Type == "distractor shot")) %>% 
  group_by(Participant) %>% 
  mutate(hitrate = (n_hit+0.5)/((n_hit+0.5)+(n_miss+0.5)), farate = (n_fa+0.5)/((n_fa+0.5)+(n_cr+0.5))) %>% 
  mutate(zscoreHit = qnorm(hitrate), zscoreFA = qnorm(farate)) %>% 
  mutate(dprime = zscoreHit - zscoreFA) %>% 
  mutate(CriterionC = -0.5*(zscoreHit+zscoreFA))

dprimes_gender1 <- raw_data %>% group_by(Participant) %>% summarise(meanrt = mean(movie_resp.rt))
dprimes_gender <- dprimes_gender %>% left_join(dprimes_gender1,by=c("Participant"))

dprimes_act <- raw_data %>% group_by(Participant,Perspective,Condition,Activity) %>% summarise(
  n_hit = sum(movie_resp.corr == 1 & Shot_Type == "test shot"),
  n_miss = sum(movie_resp.corr == 0 & Shot_Type == "test shot"),
  n_fa = sum(movie_resp.corr == 0 & Shot_Type == "distractor shot"),
  n_cr = sum(movie_resp.corr == 1 & Shot_Type == "distractor shot")
) %>% 
  group_by(Participant,Activity) %>% 
  mutate(hitrate = (n_hit+0.5)/((n_hit+0.5)+(n_miss+0.5)), farate = (n_fa+0.5)/((n_fa+0.5)+(n_cr+0.5))) %>% 
  mutate(zscoreHit = qnorm(hitrate), zscoreFA = qnorm(farate)) %>% 
  mutate(dprime = zscoreHit - zscoreFA) %>% 
  mutate(CriterionC = -0.5*(zscoreHit+zscoreFA))

dprimes1 <- raw_data %>% group_by(Participant,Perspective,Condition,Activity) %>% summarise(meanrt = mean(movie_resp.rt))
dprimes_act <- dprimes_act %>% left_join(dprimes1,by=c("Participant","Perspective","Condition","Activity"))


Image_Mact <- raw_dataIM %>% group_by(Participant,Perspective,Condition,Gender,Age,Activity) %>% summarise(accuracy_M = mean(IM_key.corr),
                                                                                                                 rt_M = mean(IM_key.rt),
                                                                                                                 rt_sd = sd(IM_key.rt))

Image_Mact$Activity <- as.factor(Image_Mact$Activity)
Image_Mact$Participant <- as.factor(Image_Mact$Participant)
levels(Image_Mact$Activity)
contrasts(Image_Mact$Activity)
```

## 4.2. Assumption check

```{r Assumptions, include=FALSE}
dprimes_gender$Gender <- ifelse(dprimes_gender$Gender == "Kadın","Female","Male")

dprimes_gender$Gender <- as.factor(dprimes_gender$Gender)
levels(dprimes_gender$Gender)
contrasts(dprimes_gender$Gender)

##### Mean RT #####

# Outlier 
dprimes_gender %>%
  group_by(Gender) %>%
  identify_outliers(meanrt)

# Shapiro wilk test
dprimes_gender %>% group_by(Participant) %>%
  group_by(Gender) %>%
  summarise(`W Stat` = shapiro.test(meanrt)$statistic,
            p.value = shapiro.test(meanrt)$p.value)

# QQ plot 
qq1 <- ggplot(data = dprimes_gender %>% group_by(Participant), mapping = aes(sample = meanrt, color = Gender, fill = Gender)) +
  stat_qq_band(alpha=0.5, conf=0.95, qtype=1, bandType = "boot") +
  stat_qq_line(identity=TRUE) +
  stat_qq_point(col="black") +
  facet_wrap(~ Gender, scales = "free") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") + theme_bw()

# Equal variances
resRT <- var.test(meanrt ~ Gender, data = dprimes_gender)
resRT

##### d primes #####

# Outlier 
dprimes_gender %>%
  group_by(Gender) %>%
  identify_outliers(dprime)

# Shapiro wilk test
dprimes_gender %>% group_by(Participant) %>%
  group_by(Gender) %>%
  summarise(`W Stat` = shapiro.test(dprime)$statistic,
            p.value = shapiro.test(dprime)$p.value)

# QQ plot 
qq2 <- ggplot(data = dprimes_gender %>% group_by(Participant), mapping = aes(sample = dprime, color = Gender, fill = Gender)) +
  stat_qq_band(alpha=0.5, conf=0.95, qtype=1, bandType = "boot") +
  stat_qq_line(identity=TRUE) +
  stat_qq_point(col="black") +
  facet_wrap(~ Gender, scales = "free") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") + theme_bw()

# Equal variances
res_d <- var.test(dprime ~ Gender, data = dprimes_gender)
res_d

##### Image memory accuracy #####

Image_M_gender <- raw_dataIM %>% group_by(Participant,Gender,Age) %>% summarise(accuracy_M = mean(IM_key.corr),
                                                                                               rt_M = mean(IM_key.rt),
                                                                                               rt_sd = sd(IM_key.rt))

Image_M_gender$Gender <- ifelse(Image_M_gender$Gender == "Kadın","Female","Male")
Image_M_gender$Gender <- as.factor(Image_M_gender$Gender)
levels(Image_M_gender$Gender)
contrasts(Image_M_gender$Gender)

# Outlier 
Image_M_gender %>%
  group_by(Gender) %>%
  identify_outliers(accuracy_M)

# Shapiro wilk test
Image_M_gender %>% group_by(Participant) %>%
  group_by(Gender) %>%
  summarise(`W Stat` = shapiro.test(accuracy_M)$statistic,
            p.value = shapiro.test(accuracy_M)$p.value)

# QQ plot 
qq3 <- ggplot(data = Image_M_gender %>% group_by(Participant), mapping = aes(sample = accuracy_M, color = Gender, fill = Gender)) +
  stat_qq_band(alpha=0.5, conf=0.95, qtype=1, bandType = "boot") +
  stat_qq_line(identity=TRUE) +
  stat_qq_point(col="black") +
  facet_wrap(~ Gender, scales = "free") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") + theme_bw()

# Equal variances
res_Acc <- var.test(accuracy_M ~ Gender, data = Image_M_gender)
res_Acc

##### Image memory RT #####

# Outlier 
Image_M_gender %>%
  group_by(Gender) %>%
  identify_outliers(rt_M)

# Shapiro wilk test
Image_M_gender %>% group_by(Participant) %>%
  group_by(Gender) %>%
  summarise(`W Stat` = shapiro.test(rt_M)$statistic,
            p.value = shapiro.test(rt_M)$p.value)

# QQ plot 
qq4 <- ggplot(data = Image_M_gender %>% group_by(Participant), mapping = aes(sample = rt_M, color = Gender, fill = Gender)) +
  stat_qq_band(alpha=0.5, conf=0.95, qtype=1, bandType = "boot") +
  stat_qq_line(identity=TRUE) +
  stat_qq_point(col="black") +
  facet_wrap(~ Gender, scales = "free") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") + theme_bw()

# Equal variances
res_rtİm <- var.test(rt_M ~ Gender, data = Image_M_gender)
res_rtİm


all_qqs <- ggarrange(qq1, qq2, qq3, qq4 + rremove("x.text"), 
                         labels = c("A)", "B)","C)","D)"),
                         ncol = 2, nrow = 2, legend= "none");all_qqs
```

## 4.3. Anaylsis

### 4.3.1 Mann-Whitney U tests

```{r Mann-whitney u}
H1<-wilcox.test(meanrt ~ Gender, data=dprimes_gender, na.rm=TRUE, paired=FALSE, exact=FALSE, conf.int=TRUE)
print(H1)

H2<-wilcox.test(dprime ~ Gender, data=dprimes_gender, na.rm=TRUE, paired=FALSE, exact=FALSE, conf.int=TRUE)
print(H2)

H3<-wilcox.test(accuracy_M ~ Gender, data=Image_M_gender, na.rm=TRUE, paired=FALSE, exact=FALSE, conf.int=TRUE)
print(H3)

H4<-wilcox.test(rt_M ~ Gender, data=Image_M_gender, na.rm=TRUE, paired=FALSE, exact=FALSE, conf.int=TRUE)
print(H4)
```

### 4.3.2 Age correlations

```{r Corr Age}
## Video memory ##

# d primes

cor.test(dprimes_gender$dprime, dprimes_gender$Age)

# meanrt

cor.test(dprimes_gender$meanrt, dprimes_gender$Age)

## Image memory ##

# accuracy

cor.test(Image_M_gender$accuracy_M, Image_M_gender$Age)

# rt

cor.test(Image_M_gender$rt_M, Image_M_gender$Age)

```

## 4.4. One way ANOVAs for Activity

### 4.4.1. Image memory
```{r Activity IM}
# Accuracy

model<-ezANOVA(data=Image_Mact,
              dv = accuracy_M,
              wid=Participant,
              within = Activity,
              detailed = TRUE,
              return_aov = TRUE,
              type=3);model
# RT

model<-ezANOVA(data=Image_Mact,
               dv = rt_M,
               wid=Participant,
               within = Activity,
               detailed = TRUE,
               return_aov = TRUE,
               type=3);model
```

### 4.4.2. Video memory

```{r Activity VD}
#dprime

dprimes_act$Activity <- as.factor(dprimes_act$Activity)
levels(dprimes_act$Activity)
contrasts(dprimes_act$Activity)

model<-ezANOVA(data=dprimes_act,
               dv = dprime,
               wid=Participant,
               within = Activity,
               detailed = TRUE,
               return_aov = TRUE,
               type=3);model

# RT
model<-ezANOVA(data=dprimes_act,
               dv = meanrt,
               wid=Participant,
               within = Activity,
               detailed = TRUE,
               return_aov = TRUE,
               type=3);model
```

